---
title: "Stats Testing & Graphs"
author: "William Irvin"
output: html_document
---

Assumptions:
Note I am only running linear regression and Chi-Sq tests, therefore I cannot really 'test' Chisq assumptions due to the nature of the data. However, to confirm qualitative things,
Period is categorical (discrete numeric), while NNRTI and NRTI are percentages (proportions) and fit into this kind of test. 
Data is assumed to be independent with no cross-counting (likelihood is very low especially considering large time frame and lack of retraction on the papers)

```{r chi}
chisq.test( table(clean_resistance$Period, clean_resistance$NNRTI) )
chisq.test( table(clean_resistance$Period, clean_resistance$NRTI) )
#Do it seperately for regions? Results might change? Focus on key regions---Asia and Africa
```


```{r LM}
model_nrt <- lm(mean_NRTI ~ Palma.ratio..Pretax...Estimated., 
               data = avg_table)
plot(model_nrt)
summary(model_nrt)


model_nnrt <- lm(mean_NNRTI ~ Palma.ratio..Pretax...Estimated., 
               data = avg_table)
plot(model_nnrt)
summary(model_nnrt)

#For the assumptions tested, both plots closely follow the Q-Q residuals plot indicating normality of the residuals, residuals v. fitted is mostly straight indicating linearity (might talk to Dr. Richards about if the limits for interpretation here), and finally scale-location is a mostly flat line for both indicating homodesacitcity of residuals. 
```

Graphs will likely be trend-line linear graphs comparing Palma Ratio/Period to NNRTI and NRTI 
